The title

### 2024-08-27 05_Manuscript/manuscript.Rmd
updating structure and data

# Methods

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

@@

We used `r cite_r("r-references.bib")` for all our analyses.

@@

>>>>

# Method

@@

@@

```{r libraries}
library(rio)
library(dplyr)
set.seed(8943)
```

```{r load-data}
sona <- import("../03_Data/sona_data.csv")
mturk <- import("../03_Data/mturk_data.csv")
```

### 2024-08-27 05_Manuscript/manuscript.tex
updating structure and data

Introduction

(Wickham, François, Henry, Müller, \& Vaughan, 2023)

@@

>>>>

\#Introduction

Example citation: (Wickham, François, Henry, Müller, \& Vaughan, 2023)

@@

Preliminary Outline

Erikson's theory and generativity.

Current measures of generativity are more about domains of generativity, actions, trait. Loyola Generativity Scale

Lacking measure of the underlying motivation, thought to be related to a motive to expand the sense of self beyond the lifetime (Kotre 1984). This is related to sense of symbolic immortality (Lifton 1979).

Terror Management Theory and generativity.

Only current scale to measure sense of immortality is Drolet's (1990) Sense of Symbolic Immortality scale. This has not been tested in translation.
